---
title: "HW 3"
subtitle: "https://github.com/bonetati/ENVS-193DS_homework-03"
format: html
---

```{r setup}
library(tidyverse)
library(here)
library(gt) 
library(janitor)
library(readxl)

# Read in data
personal_data <- read_csv(here("data", "193data.csv"))
```
1a.
I could calculate the mean stress level for each day of the week to understand if certain days are more stressful. This is informative because I suspect that weekdays, especially Mondays, are more stressful due to academic or work responsibilities, while weekends are probably less stressful.

```{r 1b}
ggplot(personal_data, aes(x = 
factor(
  Day_of_Week,
  levels = c("Saturday", "Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
), y = Stress_Level, fill = Day_of_Week)) +
  geom_jitter(width = 0.2, alpha = 0.4) +
  stat_summary(fun = mean, geom = "col", alpha = 0.6, color = "black") +
  scale_fill_brewer(palette = "Set2") +
  labs(
    title = "Average Stress Level by Day of the Week",
    x = "Day of the Week",
    y = "Stress Level"
  ) +
  theme_minimal()

```

1c.
Figure 1. This figure shows the distribution and mean of my self reported stress levels by day of the week. Bars represent the average stress level for each day, while points show individual daily reports.

```{r 1d}
personal_data %>%
  group_by(Day_of_Week) %>%
  summarize(`Average Stress Level` = round(mean(Stress_Level, na.rm = TRUE), 1)) %>%
  rename(`Day of Week` = Day_of_Week) %>%
  arrange(factor(`Day of Week`, levels = c("Saturday", "Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))) %>%
  gt() %>%
  tab_header(
    title = "Average Stress Level by Day of the Week",
  )
```



